<header style="text-align: center">

### 2019-05-24 report/report.Rmd
Add before/after/during traffic info and plot in nearby airports

- EBCI (Brussels South Charleroi)
- EBLF (Liège)
- EHEH (Eindhoven)
- EBAW (Antwerp)
- LFQQ (Lille)

@@

```{r, fig.align='center', fig.height=2.5}
ddr.times(data$real$flights, 'EBCI', event, group = 'nearby')
# ddr.times(data$real$flights, 'EBLF', event, group = 'nearby')
ddr.times(data$real$flights, 'EHEH', event, group = 'nearby')
ddr.times(data$real$flights, 'EBAW', event, group = 'nearby')
ddr.times(data$real$flights, 'LFQQ', event, group = 'nearby')
```

- Find average before/after (get % difference)

>>>>

- EBCI (Brussels South Charleroi)
- EBLG (Liège)
- EBAW (Antwerp)
- EHEH (Eindhoven)
- LFQQ (Lille)

@@

```{r, fig.align='center', fig.height=2.5}
ddr.times(data$real$flights, nearby[1], event, group = 'nearby')
ddr.times(data$real$flights, nearby[1], event, group = 'nearby')
ddr.times(data$real$flights, nearby[2], event, group = 'nearby')
ddr.times(data$real$flights, nearby[4], event, group = 'nearby')
ddr.times(data$real$flights, nearby[5], event, group = 'nearby')
```

```{r, fig.align='center'}
ggplot(data = NULL, aes(y = N.x + N.y)) +
	geom_boxplot(data = befores, aes(x = orig, color = 'before')) +
	geom_boxplot(data = durings, aes(x = orig, color = 'during')) +
	geom_boxplot(data = afters, aes(x = orig, color = 'after')) +
	scale_color_manual(limits = c('before', 'during', 'after'), values = c('green', 'red', 'blue'),
					   name = NULL, labels = c('Before the attack', paste('While', bru, 'closed'),
					   						   paste('After', bru, 'reopens'))) +
	labs(title = 'Average Daily Flights in Nearby Airports', x = NULL, y = 'Number of Flights') +
	theme(plot.title = element_text(hjust = 0.5), legend.position = 'bottom')
```

```{r, results='asis'}
for (airport in nearby) {
	cat(paste('-', airport, 'traffic:\n\t*', paste0(sprintf('%+.1f', (afters[orig == airport, mean(N.x + N.y)] - befores[orig == airport, mean(N.x + N.y)]) / befores[orig == airport, mean(N.x + N.y)] * 100), '%'), 'while', bru, 'was closed with respect to before the attack\n\t*', paste0(sprintf('%+.1f', (durings[orig == airport, mean(N.x + N.y)] - befores[orig == airport, mean(N.x + N.y)]) / befores[orig == airport, mean(N.x + N.y)] * 100), '%'), 'after', bru, 'reopens with respect to before the attack\n'))
}
```
